Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-10 Milestone_1/01-chap1.Rmd
add structure of report

# Research Problem

@@

# Overview of the Thesis

@@

# Automatic Visual Statistical Inference for linear regression diagnostics

@@

# General-Purpose Automatic Visual Statistical Inference System

@@

# Automatic Visual Infernce for Predictive Model Diagnostics

>>>>

## Structure of the Report

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{#se:project-1} presents the human subject experiments conducted in the first project along with the prototype of the automatic visual inference system. Chapter \ref{se:project-2}

<!-- presents an almost finished paper and its associated R package, ferrn, on visual diagnostics of projection pursuit optimisation. Chapter 3 introduces the stochastic optimal control problem and proposes visual diagnostics for its optimisers. Chapter 4 describes the interpretability of stochastic optimal control for decision making. And lastly, Chapter 5 outlines the timeline for future work. -->

# Research Problem {#se:research-problem}

@@

# Overview of the Thesis {se:overview}

@@

# Automatic Visual Statistical Inference for linear regression diagnostics {#se:project-1}

@@

# General-Purpose Automatic Visual Statistical Inference System {#se:project-2}

@@

# Automatic Visual Infernce for Predictive Model Diagnostics {#se:project-3}

### 2022-03-10 Milestone_1/_book/thesis.tex
add structure of report

\hypertarget{research-problem}{%
\chapter{Research Problem}\label{research-problem}}

@@

\hypertarget{overview-of-the-thesis}{%
\chapter{Overview of the Thesis}\label{overview-of-the-thesis}}

@@

\hypertarget{automatic-visual-statistical-inference-for-linear-regression-diagnostics}{%
\chapter{Automatic Visual Statistical Inference for linear regression diagnostics}\label{automatic-visual-statistical-inference-for-linear-regression-diagnostics}}

@@

\hypertarget{general-purpose-automatic-visual-statistical-inference-system}{%
\chapter{General-Purpose Automatic Visual Statistical Inference System}\label{general-purpose-automatic-visual-statistical-inference-system}}

@@

\hypertarget{automatic-visual-infernce-for-predictive-model-diagnostics}{%
\chapter{Automatic Visual Infernce for Predictive Model Diagnostics}\label{automatic-visual-infernce-for-predictive-model-diagnostics}}

>>>>

\hypertarget{structure-of-the-report}{%
\section{Structure of the Report}\label{structure-of-the-report}}

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{#se:project-1} presents the human subject experiments conducted in the first project along with the prototype of the automatic visual inference system. Chapter \ref{se:project-2}

\hypertarget{se:research-problem}{%
\chapter{Research Problem}\label{se:research-problem}}

@@

\hypertarget{overview-of-the-thesis-seoverview}{%
\chapter{Overview of the Thesis \{se:overview\}}\label{overview-of-the-thesis-seoverview}}

@@

\hypertarget{se:project-1}{%
\chapter{Automatic Visual Statistical Inference for linear regression diagnostics}\label{se:project-1}}

@@

\hypertarget{se:project-2}{%
\chapter{General-Purpose Automatic Visual Statistical Inference System}\label{se:project-2}}

@@

\hypertarget{se:project-3}{%
\chapter{Automatic Visual Infernce for Predictive Model Diagnostics}\label{se:project-3}}
